Examining Crowd Work and Gig Work Through The Historical Lens of Piecework

### 2017-05-02 chi/piecework/presentation/presentation.tex
svgs
monday updates; finished intro?

\usepackage{tikz,lmodern,textpos,hyperref,graphicx,booktabs,appendixnumberbeamer,nth,xcolor,svg}
\usepackage[citestyle=numeric,backend=bibtex]{biblatex}
\usepackage[export]{adjustbox}
\usepackage[en-US]{datetime2}
\bibliography{references}
\usetheme{metropolis}
\beamertemplatenavigationsymbolsempty
\renewcommand\textbullet{\ensuremath{\bullet}}
\definecolor{stanfordRed}{HTML}{8C1515}
% \mode<presentation>{
  % \usetheme{metropolis}
  \usecolortheme{seagull}

@@

\begin{document}

\begin{frame}
\titlepage
\end{frame}
% \renewcommand\multicitedelim{\addsemicolon\space}

@@

\section*{Introduction}

% \begin{frame}[t]{Open problems in crowdsourcing}
%   \begin{itemize}[<+>]
%     \item \textbf{Complexity}~\textcite{suzukiAtelier,KimStoria,yuanAlmost,
%                            Nebeling:2016:WCW:2858036.2858169,
%                            Hahn:2016:KAB:2858036.2858364}
%   \end{itemize}
% \end{frame}

% \begin{frame}[t]{Open problems in crowdsourcing}
%   \begin{itemize}[<+>]
%     \item \textbf{Complexity}~\textcite{suzukiAtelier,KimStoria,yuanAlmost,
%                            Nebeling:2016:WCW:2858036.2858169,
%                            Hahn:2016:KAB:2858036.2858364}
%     \item \textbf{Decomposition}~\textcite{sensitiveTasks,LykourentzouPersonalityMatters,
%                               Law:2016:CKC:2858036.2858144,
%                               Chang:2016:ACC:2858036.2858411,
%                               Newell:2016:OMA:2858036.2858490}
%   \end{itemize}
% \end{frame}

\begin{frame}[t]{Open problems in crowdsourcing}
\begin{columns}
\begin{column}{0.6\textwidth}
  \begin{itemize}%[<+>]
    \item<1,4> \textbf{Complexity}~\textcite{suzukiAtelier,KimStoria,yuanAlmost,
                           Nebeling:2016:WCW:2858036.2858169,
                           Hahn:2016:KAB:2858036.2858364}
    \item<2> \textbf{Decomposition}~\textcite{sensitiveTasks,LykourentzouPersonalityMatters,
                              Law:2016:CKC:2858036.2858144,
                              Chang:2016:ACC:2858036.2858411,
                              Newell:2016:OMA:2858036.2858490}
    \item<3> \textbf{Relationships}~\textcite{turkopticon,storiesIraniSilberman,crowdcollab,
                              takingAHITMcInnis}

  \end{itemize}

\end{column}
\begin{column}{0.4\textwidth}
test
\end{column}
\end{columns}
%   \begin{figure}[htbp]
%   \centering

% \end{figure}

  % \begin{figure}
  % \includesvg{test}
  % \caption{svg image}
  % \includegraphics<1>[width=.5\textwidth]{figures/handy.png}
  % \includegraphics<2>[width=.5\textwidth]{figures/amt.png}
  % \includegraphics<3>[width=.5\textwidth]{figures/uber.png}
  % \end{figure}
\end{frame}

\begin{frame}[standout]{whataatatat}
    What is the future of work?

>>>>

\usepackage{tikz,lmodern,textpos,hyperref,graphicx,booktabs,appendixnumberbeamer,nth,xcolor,svg,subfiles}
\usepackage[citestyle=numeric,backend=bibtex]{biblatex}
\usepackage[export]{adjustbox}
\usepackage[en-US]{datetime2}
\bibliography{references}
\usetheme{metropolis}
\beamertemplatenavigationsymbolsempty
\renewcommand\textbullet{\ensuremath{\bullet}}
\definecolor{stanfordRed}{HTML}{8C1515}
% \mode<presentation>{
  % \usetheme{metropolis}
  \usecolortheme{seagull}

@@

\newcommand{\onlyinsubfile}[1]{#1}
\begin{document}
\renewcommand{\onlyinsubfile}[1]{}
\begin{frame}
\titlepage
\end{frame}
% \renewcommand\multicitedelim{\addsemicolon\space}

@@

% \subfile{intro.tex}

\begin{frame}[standout]
    What is the future of work?
